Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-07 paper.tex
added alternative figure at bottom of the article
Moved alternate fig 'in our heads' next to the other one for easier comparison

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
    \caption{Anthropomorphism is a psychological phenomenon which arises in a
        social context, during an
    interaction between a human agent and a non-human agent. One can take two main perspectives when trying to explain
    anthropomorphism: a human-centered and an artifact-centered perspective (grey
    triangles). Several external factors influence the anthropomorphism
    phenomenon. Person- and artifact-related characteristics, but also related to the
context of use as well as the actual time spent interacting with the robot (interaction history).}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
    \caption{Anthropomorphism is a psychological phenomenon which arises in a
        social context, during an interaction between a human agent and a
        non-human agent. One can take two main perspectives when trying to
        explain anthropomorphism: a human-centered and an artifact-centered
        perspective (grey triangles). Several external factors influence the
        anthropomorphism phenomenon. Person- and artifact-related characteristics,
        but also related to the context of use as well as the actual time spent
        interacting with the robot (interaction history). [SEE
        FIG~\ref{fig:anthropofig-alt} FOR AN ALTERNATIVE FIGURE]}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
        subjective, psychological phenomenon which arises in a social context, during an
        interaction between a human agent and a non-human agent. One can take
        two main perspectives when trying to explain anthropomorphism: a
        human-centered and an artifact-centered perspective.
        Several external factors influence the anthropomorphism phenomenon.
        Person- and artifact-related characteristics, but also related to the
        context of use as well as the actual time spent interacting with the
        robot (interaction history).}

    \label{fig:anthropofig-alt}
\end{figure}
